---
title: "Week 02: COVID Visualization Activity"
author: "**`[[`**Your Name**`]]`**"
format: gfm
---

Today, we'll be working with a data set related to COVID.
This data is based on data from the the [COVID Tracking Project](https://covidtracking.com/).
I cleaned up this data and also added total populations from the 2020 for each of the relevant categories.
Note, due to differences in the way race and ethnicity are encoded in the census as compared to the the COVID Tracking Project, the population counts for LatinX may be somewhat inaccurate.

```{r load_data}
library(tidyverse)
load("CRDT Data.RData")
ls()
```

I've include 4 different data sets.
They all have the same data but have it represented in different ways.
Try using the different data sets and see which ones are good for making which plots.


```{r first_plot}
ggplot(covid_data_count, aes(x = date, y = Cases)) + geom_point()
```



If you want to only look at a specific state, you can do it like this.
For now, see what you can do just using `ggplot`.

```{r}
covid_data_count |> 
  filter(state %in% c("MA", "MD")) |> 
  ggplot(aes(x = date, y = Cases, color = race)) + geom_line()
```
```{r}
ggplot(covid_data_count, aes(x = state_name, y = Cases/population)) + geom_bar(stat = "identity", fill = "pink") + theme(axis.text.x = element_text(angle = 60, hjust = 1))
```
```{r}
ggplot(covid_data_count, aes(x = date)) +
  geom_line(aes(y = Cases, color = "Cases")) +
  geom_line(aes(y = Deaths, color = "Deaths")) +
  scale_color_manual(values = c("Cases" = "blue", "Deaths" = "red"))
```


1. After making and refining some plots, pick one and save the code and describe what you observe?
I made a plot for stat vs the percentage of cases to population. I noticed from this is that lousiana, utahm and south dakota had the highest cases to population ratio whereas even for states like cali which have the most cases actually have a generally pretty low case to population ratio.

2. What conclusions can you draw?
Population isnt the sole factor in determining case to population ratio and perhaps theres ia correlation between prevention efforts and ratio more.

3. What were you not able to do due to not having the coding knowledge?
I wasnt able to filter out the states to only show the top 10 states instead of all 50.

4. What made previous plots you made hard to interpret/understand? What did you do to improve/change them to ease interpretation?
I played around the orientation of the axes for the ones where I plotted state names so that I could read the state names. I rotated the names.

5. What other data would be useful to better understand this data?
It would be nice to see factors like education levels, or vaccine rates.

